---
title: "Introduction to madmR"
author: "Blake Conrad"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Core Functions
<ul>
  <li>read.data.matrix(..)</li>
  <li>TOPSIS(...)</li>
  <li>MAUT(...)</li>
  <li>sensitivity(...)</li>
</ul>
```{r}
library(ggplot2)
library(madmR)
```

## Reading in data matrices
The general format for any decision matrix is N rows by D columns. Decision analysts almost always exempt row 1 as the row to enforce attribute weighting, so this is also enforced in  read.data.matrix() function. Additionally, enforcing columns as benefits or costs is paramount in decision analysis, so this is also brutally enforced in the read function; I.e., any attributes which do not contain the word 'cost' in them will be treated as benefit.
```{r}
#maut_dm   <- read.data.matrix("Data/maut_validate_benefits.csv", header=TRUE)
#topsis_dm <- read.data.matrix("Data/topsis_validate_benefits.csv", header=TRUE)
```

## These data are already pre-loaded with the package for testing and examples
```{r}
data(maut_dm)
data(topsis_dm)
```

## A simple TOPSIS example
```{r}
topsisResults <- TOPSIS(topsis_dm) #version 0.0.0.1000 has no additional parameters
topsisResults$Results
```

## A simple MAUT example
```{r}
mautResults <- MAUT(maut_dm)
mautResults$Results
```

## A simple sensitivity example
Since we know there are no additional parameters for the topsis function, we can run it without concerning ourselves with the algParams. This will only be applicable to the MAUT algorithm.
```{r}
FinalDB <- sensitivity(data=maut_dm)
FinalDB$Results          # Output from all the runs
FinalDB$EdgeCasesResults # Show all of the cases in Final_DB$Results which rank changed
```

## More Examples
TOPSIS
```{r}
dm <- TOPSIS(topsis_dm)
dm
```
MAUT
```{r}
dm <- MAUT(maut_dm, 
           scales=c("linear","linear","exponential") #default to all linear
           )
dm
```
Sensitivity
```{r, fig.show='hold'}
# All attributes, specific step size, only 1 algorithm, algorithm specified parameters
FinalDB <- sensitivity(data=topsis_dm,
                       step=0.1,
                       algs="MAUT",
                       algParams=list(MAUT=list(scales=list("linear",
                                                            "linear",
                                                            "linear",
                                                            "exponential",
                                                            "exponential",
                                                            "exponential",
                                                            "linear")))
                       )
FinalDB$Plot
```

# Specific attributes, specific step size, algorithm specific parameters
```{r}
FinalDB <- sensitivity(data=maut_dm,
                       attr=c("Sq.Foot","Preference"),
                       step=0.01,
                       algParams=list(MAUT=list(scales=list("linear",
                                                            "linear",
                                                            "exponential")))
                       )
FinalDB$Plot
```

# Single attribute, specific step size, specific algorithms, specific window to study that attribute on.
```{r}
FinalDB <- sensitivity(data=maut_dm,
                       attr="Sq.Foot",
                       algs=c("TOPSIS", "MAUT"),
                       step=0.01,
                       window=c(0.1,0.5)
                       )
FinalDB$Plot
```

